Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
ok

```{r duplicates, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
# DUPLICATE FRACTION
df <- df.combined.preprocessed %>% group_by(catalog) %>%
      			           summarise(duplicates = 100 * mean(remove))
p <- ggplot(df, aes(x = catalog, y = duplicates)) +
       geom_bar(position = "dodge", stat = "identity") +
       ylab("Duplicates (%)") +
       ggtitle(paste("Duplicates", paste(range(df.combined.preprocessed$publication_year), collapse = "-")))
print(p)
```

>>>>

```{r duplicates, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
# DUPLICATE FRACTION
df <- df.combined.preprocessed %>% group_by(catalog) %>%
      			           summarise(duplicates = 100 * mean(remove))
p <- ggplot(df, aes(x = catalog, y = duplicates)) +
       geom_bar(position = "dodge", stat = "identity") +
       ylab("Duplicates (%)") +
       ggtitle(paste("Duplicates", paste(range(df.combined.preprocessed$publication_year), collapse = "-")))
print(p)

df <- df.combined.preprocessed %>% group_by(catalog) %>%
      			           summarise(duplicates = 100 * mean(remove))
p <- ggplot(df, aes(x = catalog, y = duplicates)) +
       geom_bar(position = "dodge", stat = "identity") +
       ylab("Duplicates (%)") +
       ggtitle(paste("Duplicates", paste(range(df.combined.preprocessed$publication_year), collapse = "-")))
print(p)
```
